---
title: "Sphagnum_regression_peat_tissue_respiration"
output: html_document
---

We previously ran a basic FvCB tunned to Sphagnum that did NOT account for dead peat respiration. 

Here, we look at correcting that by first using a linear regression model to estimate peat respiration from temperature using the cut chambers (those chambers that had live SPhagnum cut from them). 

```{r, echo=FALSE, results='hide'}
setwd("~/Desktop/SPRUCE_paper")
data1<-read.csv("SPRUCE_LI8100_2014_Env_Combined_all.csv")
head(data1)
tail(data1)
summary(data1)
library(dplyr)
library(ggvis)
dat.df<-tbl_df(data1)
names(dat.df)
```

determine hetertrophic respiration as a linear regression of bare plots by temp
    
```{r, echo=FALSE}

df.select<-select(dat.df, DFOY, Binned.Time.of.Day,IV.Tcham, Temp.C, PAR, IV.RH,Exp_Flux_Corr, Mean.Sph.Temp.0cm, DOY, IV.CO2, Port.)
df.filter<-filter(df.select,DOY > 240, Mean.Sph.Temp.0cm >=0, Port. == 2)
temp <-df.filter$Mean.Sph.Temp.0cm 
flux <- df.filter$Exp_Flux_Corr

lm.heterotroph <- lm(flux ~ temp)
summary(lm.heterotroph)

```

Here is a plot of the predicted values from the observed for the cut bare plots for bar plot flux by predicted values

```{r, echo=FALSE}
pred.flux<-predict(lm.heterotroph)
plot(flux, pred.flux, xlim=c(0,2), col='dark gray')

```

How does this compare to night time values for bare plots, and night time values for plots with live sphagnum?

First, the bare plots night temp vs. predcition values 

```{r, echo=FALSE}

df.select<-select(dat.df, DFOY, Binned.Time.of.Day,IV.Tcham, Temp.C, PAR, IV.RH,Exp_Flux_Corr, Mean.Sph.Temp.0cm, DOY, IV.CO2, Port.)
filter.night<-filter(df.select,DOY > 240, Binned.Time.of.Day =="Night", Mean.Sph.Temp.0cm >=0, Port. == 2)
temp.night <-filter.night$Mean.Sph.Temp.0cm 
flux.night <- filter.night$Exp_Flux_Corr

lm.heterotroph.night <- lm(flux.night ~ temp.night)
summary(lm.heterotroph.night)

pred.flux.night<-predict(lm.heterotroph.night)
plot(flux.night, pred.flux.night, xlim=c(0,2), col='dark gray')

```


Now lets compare the predicted vlaues to night time chambers values with Sphagnum. this will have plant dark respiration values. Test with chamner 4

```{r, echo=FALSE, results='hide'}
a<-dat.df %>%
    select(DFOY, Binned.Time.of.Day,IV.Tcham, Temp.C, PAR, IV.RH,Exp_Flux_Corr, Mean.Sph.Temp.0cm, DOY, IV.CO2, Port.) %>%
    filter(DOY > 240, Binned.Time.of.Day =="Night", Mean.Sph.Temp.0cm >=0, Port. == 4) %>%
    mutate(pred.values = 0.171073 + 0.061759*Mean.Sph.Temp.0cm)

    plot(a$Exp_Flux_Corr, a$pred.values, xlim=c(0,2), col='dark gray')
```

Now lets compare the predicted vlaues to night time chambers values with Sphagnum. this will have plant dark respiration values. Test with chamner 5


```{r, echo=FALSE, results='hide'}
b<-dat.df %>%
    select(DFOY, Binned.Time.of.Day,IV.Tcham, Temp.C, PAR, IV.RH,Exp_Flux_Corr, Mean.Sph.Temp.0cm, DOY, IV.CO2, Port.) %>%
    filter(DOY > 240, Binned.Time.of.Day =="Night", Mean.Sph.Temp.0cm >=0, Port. == 5) %>%
    mutate(pred.values = 0.171073 + 0.061759*Mean.Sph.Temp.0cm)

    plot(b$Exp_Flux_Corr, b$pred.values, xlim=c(0,2), col='dark gray')
```


Now lets compare the predicted vlaues to night time chambers values with Sphagnum. this will have plant dark respiration values. Test with chamner 6


```{r, echo=FALSE, results='hide'}
c<-dat.df %>%
    select(DFOY, Binned.Time.of.Day,IV.Tcham, Temp.C, PAR, IV.RH,Exp_Flux_Corr, Mean.Sph.Temp.0cm, DOY, IV.CO2, Port.) %>%
    filter(DOY > 240, Binned.Time.of.Day =="Night", Mean.Sph.Temp.0cm >=0, Port. == 5) %>%
    mutate(pred.values = 0.171073 + 0.061759*Mean.Sph.Temp.0cm)

    plot(c$Exp_Flux_Corr, c$pred.values, xlim=c(0,2), col='dark gray')
```


So its possible there is a tissue respiration signal that is distinguishable from peat respiration. Will look at this with some simple cumsum plots. 

daily night time averge for 2 clip plots vs non-clipped. 

