---
title: "Sphagum_GPP"
output: html_document
---

Calculation of GPP: as a f(mean_night_CO2 - mean_day_CO2)

```{r, echo=FALSE, results='hide'}
setwd("~/GitHub/Sphagnum_FvCB")
data1<-read.csv("SPRUCE_LI8100_2014_Env_Combined_all.csv")
head(data1)
tail(data1)
summary(data1)
library(dplyr)
library(ggvis)
dat.df<-tbl_df(data1)
names(dat.df)
```


This is the average valuer per day for each of chambers 3-6, then summed for all 4 chambers over the year.


```{r}

night_GPP<-dat.df %>%
    select(Port., DFOY, DOY, Exp_Flux_Corr, Binned.Time.of.Day) %>%
    filter(Binned.Time.of.Day=="Night", Exp_Flux_Corr > 0, Port. >=3) %>%
    group_by(DOY, Port.) %>%
    summarise(night_mean = mean(Exp_Flux_Corr))

day_GPP<-dat.df %>%
    select(Port., DFOY, DOY, Exp_Flux_Corr, Binned.Time.of.Day) %>%
    filter(Binned.Time.of.Day=="Midday", Exp_Flux_Corr < 0, Port. >=3) %>%
    group_by(DOY, Port.) %>%
    summarise(day_mean = mean(Exp_Flux_Corr))
              
head(night_GPP)
dim(night_GPP)
colSums(night_GPP[,3])
colSums(day_GPP[,3])

```



So its possible there is a tissue respiration signal that is distinguishable from peat respiration. Will look at this with some simple cumsum plots. 

daily night time averge for 2 clip plots vs non-clipped. 

This is for DOY > 240
```{r}

night_GPP_clipped<-dat.df %>%
    select(Port., DFOY, DOY, Exp_Flux_Corr, Binned.Time.of.Day) %>%
    filter(Binned.Time.of.Day=="Night", Exp_Flux_Corr > 0, Port. <=2, DOY >=240) %>%
    group_by(DOY, Port.) %>%
    summarise(night_clip_mean = mean(Exp_Flux_Corr))

Night_GPP_not_clipped<-dat.df %>%
    select(Port., DFOY, DOY, Exp_Flux_Corr, Binned.Time.of.Day) %>%
    filter(Binned.Time.of.Day=="Night", Exp_Flux_Corr > 0, Port. >=3, DOY >=240) %>%
    group_by(DOY, Port.) %>%
    summarise(night_unclip_mean = mean(Exp_Flux_Corr))
              
head(night_GPP_clipped)
head(Night_GPP_not_clipped)

Ave_per_port_night_clipped<- colSums(night_GPP_clipped[,3])/2
Ave_per_port_night_unclipped <- colSums(Night_GPP_not_clipped[,3])/4

Ave_per_port_night_clipped
Ave_per_port_night_unclipped

```

Transient code... looking at paired chambers (1 & 5) pre-cut and after cut.

```{r}

night_GPP_clipped<-dat.df %>%
    select(Port., DFOY, DOY, Exp_Flux_Corr, Binned.Time.of.Day) %>%
    filter(Binned.Time.of.Day=="Night", Exp_Flux_Corr > 0, Port. ==1, DOY > 240) %>%
    group_by(DOY, Port.) %>%
    summarise(night_clip_mean = mean(Exp_Flux_Corr))

Night_GPP_not_clipped<-dat.df %>%
    select(Port., DFOY, DOY, Exp_Flux_Corr, Binned.Time.of.Day) %>%
    filter(Binned.Time.of.Day=="Night", Exp_Flux_Corr > 0, Port. ==5, DOY > 240) %>%
    group_by(DOY, Port.) %>%
    summarise(night_unclip_mean = mean(Exp_Flux_Corr))
              
#head(night_GPP_clipped)
#head(Night_GPP_not_clipped)

Ave_per_port_night_clipped<- colSums(night_GPP_clipped[,3])
Ave_per_port_night_unclipped <- colSums(Night_GPP_not_clipped[,3])

Ave_per_port_night_clipped
Ave_per_port_night_unclipped

```


